---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cccmdown

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![R-CMD-check](https://github.com/unhcr-dataviz/cccmdown/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/unhcr-dataviz/cccmdown/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/unhcrthemes)](https://CRAN.R-project.org/package=unhcrthemes)
<!-- badges: end -->

The goal of cccmdown is to ease and speed up the creation of reports following the [CCCM brand identity](https://www.cccmcluster.org/branding-collection).

## Installation

Get started by installing the `{cccmdown}` package from GitHub using the `{pak}` library:

```{r install, eval=FALSE}
# If pak is not yet installed, uncomment the following line:
# install.packages("pak")

pak::pkg_install("unhcr-dataviz/cccmdown")
```


## Contribution and Code of Conduct

Contributions to `{cccmdown}` are highly valued.  If you have suggestions, uncover bugs, or envision new features, kindly submit an [issue on GitHub](https://github.com/unhcr-dataviz/cccmdown/issues). To contribute code, don't hesitate to fork the repository and create a pull request.

## License

This package is distributed under the [MIT License](https://github.com/unhcr-dataviz/cccmdown/blob/master/LICENSE.md).
